---
title: "test targets"
author: "Mathew Ling"
date: "30/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(here)


```

```{r read-in}
df <-  read_csv(here::here("data","reddit_vm.csv"))

```

## Target test

This report does some basic data manipulation of some anti-vax content from reddit (acquired from [kaggle](https://www.kaggle.com/gpreda/reddit-vaccine-myths)). 

The data frame contains the following variables:

- title - relevant for posts
- score - relevant for posts - based on impact, number of comments
- id - unique id for posts/comments
- url - relevant for posts - url of post thread
- commns_num - relevant for post - number of comments to this post
- created - date of creation
- body - relevant for posts/comments - text of the post or comment
- timestamp - timestamp

Convert this into a `target` pipeline that generates this same report. 

```{r cleaning}
df_cleaned <-  df %>% drop_na(body) %>% 
  select(id, body, score, comms_num, timestamp) %>% 
  group_by(id) %>% 
  unnest_tokens("words", body) %>% 
  ungroup() %>% 
  anti_join(stop_words, by = c("words"= "word"))

```

```{r frequencies}
word_freq <- df_cleaned %>% 
  count(words) %>% 
  filter(n<300&n>40) %>% 
  mutate(words = reorder(words, n))


```


## Plots

You can also embed plots, for example:

```{r plot, echo=FALSE}
word_freq_plot <-  word_freq %>% ggplot(aes(x = words, y = n)) + geom_col() + coord_flip()

word_freq_plot
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
